Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-11-13 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
added a section for ideas to improve LIME

Ideas for improvement of LIME: 
  - change the binning method

>>>>

Ideas for improvement of LIME: 
  - change the binning method:
    - lime is not good with linear relationships with classifiers due to the 
    inside-outside binning - it would be better to use a cumulative approach
  - consider interactions in the ridge regression model
  - learn lambda in the ridge regression
